Notes

### 2021-11-15 Notes.Rmd
update cleaning data + viz started draft ergms for national networks

1. Compute the import / export ratio per country
2. Same at commodity level: are there commodities that are purely trade driven?
3. Explore Paula's file: rank countries per number of companies on high risk
4. Extract main commodities
5. Characterize missing values: where are they missing (countries) and what vars are not very useful?
6. Construct networks between countries and corporations weighted by subsidiaries?

>>>>

1. Compute the import / export ratio per country
2. Same at commodity level: are there commodities that are purely trade driven?
3. ~~Explore Paula's file: rank countries per number of companies on high risk~~
4. ~~Extract main commodities~~
5. Characterize missing values: where are they missing (countries) and what vars are not very useful?
6. ~~Construct networks between countries and corporations weighted by subsidiaries?~~

Exponential random graph models:
- Include world governance indicators
- Inequality
- Triangles? Feedforward triangles -> theory on instability?
- Valued ergm with number of companes count on link weight?
